### 2018-01-22 README.Rmd
update README with publication information
add note to README; update with latest container
add poster to README.Rmd

## Preprint

> Kamvar ZN, Amaradasa BS, Jhala R, McCoy S, Steadman JR, Everhart SE. (2017) Population structure and phenotypic variation of *Sclerotinia sclerotiorum* from dry bean (*Phaseolus vulgaris*) in the United States. *PeerJ Preprints* 5:e3311v2 <https://doi.org/10.7287/peerj.preprints.3311v2>

## Data and Code

@@

>>>>

## Publication

> Kamvar ZN, Amaradasa BS, Jhala R, McCoy S, Steadman JR, Everhart SE. (2017) Population structure and phenotypic variation of *Sclerotinia sclerotiorum* from dry bean (*Phaseolus vulgaris*) in the United States. *PeerJ* 5:e4152 <https://doi.org/10.7717/peerj.4152>

> Poster presented at the 2018 National Sclerotinia Initiative: <https://doi.org/10.6084/m9.figshare.5791713>

Data and Code
-------------

@@

Note: This citation represents the data and code that was in this repository at the time of re-submission (2017-11-15 20:42 UTC), For the docker container, this represents tag v1.1. You can find the live code at <https://osf.io/ejb5y>
